A Pair of Holomorphic Fivebranes

### 2023-04-17 aone/main.tex
merge

\documentclass{amsart}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage[titletoc]{appendix}
\usepackage{hyperref}

%\usepackage{tikz} 	  % Replaced with tikz-cd, but am
\usepackage{tikz-cd}  % willing to learn tikz if necessary
	\usetikzlibrary{decorations.pathmorphing}

\usepackage[all]{xy}
\usepackage{stmaryrd}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{tabularx}

\usepackage{macros}

\renewcommand\tabularxcolumn[1]{m{#1}}
\newcolumntype{Y}{>{\centering\arraybackslash}X}

@@

>>>>

\documentclass{amsart}
%\usepackage{fullpage}
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage{amsfonts}
%\usepackage{amsthm}
%\usepackage{enumerate}
%\usepackage[titletoc]{appendix}
%\usepackage{hyperref}
%
%%\usepackage{tikz} 	  % Replaced with tikz-cd, but am
%\usepackage{tikz-cd}  % willing to learn tikz if necessary
%	\usetikzlibrary{decorations.pathmorphing}
%
%\usepackage[all]{xy}
%\usepackage{stmaryrd}
%\usepackage{indentfirst}
%\usepackage{graphicx}
%\usepackage{tabularx}

\usepackage{../macros-mtheory}

%\renewcommand\tabularxcolumn[1]{m{#1}}
%\newcolumntype{Y}{>{\centering\arraybackslash}X}

@@

\appendix

\section{Costello's treatment}

Given a super vector space $V$ one can consider the free chiral conformal field theory of spin $1/2$ fields $\psi$ taking values in $V$ and $\chi$ taking values in $V^*$.
When $V$ is purely odd then this describes a number of complex free fermions.
When $V$ is purely even this is a version of the $\beta-\gamma$ system.

Let $GL(V)$ (respectively, $\lie{gl}(V)$) be the super general linear group (respectively, Lie algebra) acting on the super vector space $V$.
Then, along a Riemann surface defect we can couple this chiral CFT to $GL(V)$ valued five-dimensional Chern--Simons theory. 
Explicitly, if we place five-dimensional Chern--Simons theory on $\R \times \C^2$ and the defect along
\beqn
0 \times \C_z \times 0 \subset \R \times \C^2
\eeqn
then the five-dimensional Chern--Simons gauge field $A \in \Omega^{0,\bu}(\R \times \C^2) \otimes \lie{gl}(V)$ couples via the Lagrangian
\beqn
\int_{\C_z} \chi (A \cdot \psi) .
\eeqn

For $N,M \geq 1$ we will take $V$ to be the dimension $N+M|M$ superspace~$\C^{N+M|M}$.
Let $\cF(N+M|M)$ be the $GL(N+M|M)$-invariants of the vertex algebra corresponding to the free CFT along the defect.
This is a sub vertex algebra of some tensor product of $M$ free $\beta-\gamma$ systems and $(N+M)$ pairs of chiral free fermions.
Notice that for $M<M'$ the decomposition $\C^{N+M'|M} = \C^{N+M|M} \oplus \C^{M'-M|M'-M}$ determines a $GL(N+M'|M')$-invariant map of vertex algebras
\beqn
\cF (N+M'|M') \to \cF(N+M|M) .
\eeqn
Denote by $\cF(N+\infty|\infty)$ the resulting limit vertex algebra
\beqn
\cF(N+\infty|\infty) = \lim_{M<M'} \left(\cF (N+M'|M') \to \cF(N+M|M) \right) .
\eeqn

Consider the algebra 
\beqn
\cO_\ep (\C^\times \times \C) 
\eeqn
which as an underlying vector space is $\C[z,z^{-1},w]$ and the commutator is the $\star_\ep$ commutator.
Viewing this as a Lie algebra, it admits a central extension that we denote by $\lie{w}_{1+\infty}(\ep)$.
We denote the central element by~$K$.
When $\ep = 1$ denote this simply by $\lie{w}_{1+\infty}$.
Notice that for $\ep \ne 0$ there is an isomorphism of Lie algebras
\beqn
\lie{w}_{1+\infty} \xto{\simeq} \lie{w}_{1+\infty}(\ep) .
\eeqn
which sends $z \mapsto z$ and $w \mapsto \ep w$.
By setting $w = \frac{\del}{\del z}$ observe that the Lie algebra $\lie{w}_{1+\infty}$ is a central extension of the Lie algebra of differential operators on $\C^\times$

Let $\lie{w}_{1+\infty}(\ep)_+$ be the subalgebra of positive modes (in the variable $z$) and consider the module
\beqn
W_{1+\infty}(\ep) \define U(\lie{w}_{1+\infty}(\ep)) \slash {U(\lie{w}_{1+\infty}(\ep)_+)} .
\eeqn
This has the natural structure of a vertex algebra in the category of $\C[K]$-modules.
For $c \in \C$ let $W_{1+\infty}(\ep,c)$ denote the vertex algebra which is the further quotient where we set the central element~$K = c$. 
For $\ep \ne 1$, and for fixed $c$, the vertex algebras $W_{1+\infty}(\ep,c)$ are all isomorphic.
Denote by $W_{1+\infty}(c) = W_{1+\infty}(1,c)$.

When $c = N$ the vertex algebra $W_{1+\infty}(N)$ admits a quotient which is isomorphic to the vertex algebra~$W_N = W(\lie{sl}(N))$.

\begin{prop}
Let $W_{1+\infty}$
There is an isomorphism of vertex algebras
\beqn
\cF(N+\infty|\infty) \simeq W_{1+\infty}(c=N) .
\eeqn
\end{prop}

\section{Higher free fermion}

Consider the line bundle on $\Sigma \times \C^2$
\beqn
L_r \define K^{r/2}_\Sigma \boxtimes \ul{\C} 
\eeqn
where $\ul{\C}$ denotes the trivial line bundle on $\C^2$.

Consider the following $\Z \times\Z/2$ complex of sheaves $\cE_r$ whose even part is
\beqn
\cE_{r}^{ev} = \Omega^{0,\bu}(\Sigma \times \C^2 , K^{1/2} \otimes L_r) .
\eeqn
And whose odd part is 
\beqn
\cE_r^{odd} = \Omega^{0,\bu}(\Sigma \times \C^2 , L)[2] \xto{\del} \Omega^{1,\bu}(\Sigma,L)[1] .
\eeqn

There is a local action of $\cE(3|6)$.

\subsection{Characters}

The character for the chiral free fermion is 
\beqn
\ch_{\bF}(q,t) = \prod_{n \geq 1} (1+t q^{n-1/2})(1+t^{-1} q^{n-1/2}) = \sum_{m \in \Z} Z_m (q) t^m .
\eeqn
From this one can see that 
\beqn
Z_0(q) = \oint \frac{\d t}{2\pi i t} \ch_{\bF}(q,t) = \prod_{n \geq 1} \frac{1}{1 - q^{n}} .
\eeqn
This is the character level version of the statement that the $\C^\times$-invariants of the chiral free fermion is equivalent to the free chiral boson.
